Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
delete unnecessary lemmas in section 3

\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_2^2\rangle.
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}

\begin{prop}
\label{prop:sat_two_induction}
Let $(\sx, \Delta, L)$ and $(\sx', \Delta, L')$ be tame separably rooted log stacky spin curves. 
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted log stacky curves so that $\sx$ has signature 
$\sigma = (g;e_1,\ldots, e_r;\delta)$ with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5,\ldots, x_m]/I'$ and let $L = L' + \frac{1}{
3}P.$ Suppose $L$ and $L'$ satisfy $sat(Eff(L')) = sat(Eff(L)) = 2.$
Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}

In a fashion analogous to the proof of Proposition 
~\ref{prop:sat_three_induction}, we see 
the following is a $k$ basis for $R$ over $R'$:

\begin{lem}
\label{lem:deg1_sat_ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $\deg(\lfloor{D}\rfloor)\ge 0$, so $R_D$ has a
generator $u$ in degree 1.  Suppose $D$ is generated by $
u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $P \not \in \Supp(D), \alpha,\beta \in \mathbf{N}$ such
that

\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
\end{align*}
In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
\end{itemize}
\end{lem}

@@

@@

\begin{prop}
\label{prop:sat_three_induction}
\todo{Make explicit assumptions on genus.}
\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction. Actually, the map isn't ramified at $P$, it's just defined away from $P$. I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $L = L' + \frac{1}{
3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and $y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
		y_4 \prec y_3$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{prop}

@@

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{prop:sat_two_induction}.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of ramified
points in Proposition ~\ref{prop:sat_three_induction} and
an inductive statement on ramification orders in Theorem
~\ref{thm:ram_order_ind}. After verifying that explicit pairs
$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, the application of the
two inductive statements demonstrate that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of a finite set of exceptional cases.

@@

Through the application of two processes of induction, by adding 
points via Proposition ~\ref{prop:sat_three_induction} and by raising
ramification orders via Theorem ~\ref{thm:ram_order_ind},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.

@@

Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
If $\sigma = (0; e_1, \ldots, e_r; 0)$ is not one of the
exceptional cases in Table ~\ref{table:g_0_exceptional} and $r \leq
5$, then $\sigma$ ``lies above'' one of the base cases of Lemma
~\ref{lem:g_0_admissible_cases}. In other words, one of the base
cases $(\sigma', J)$ with $\sigma' = (0; e_1', \ldots, e_r'; 0)$
satisfies the property that for all $i \in J$, $e_i \geq e_i'$ and
$e_i = e_i'$ otherwise. If $r > 5$, then we can use Proposition
~\ref{prop:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$, since the
saturation in this case is equal to $3$.

@@

%By Lemma ~\ref{lem:g_0_admissible_cases}, we know that for
%any tame log spin curves $(\sx', \Delta, \halfcan')$ over a perfect
%field $k$ with signature $\sigma'$ and set $J$ such that $(\sigma',
%J)$ is one of the listed base cases, $(\sigma', J)$ is admissible.
%Furthermore, $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k
%$- algebra by elements of degree at most $e = \max(5, e_1, \ldots, e
%_r)$ with relations in degree at most $2e$. It also admits a
%presentation
%
%\begin{align*}
	%R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
%\end{align*}
%
%\noindent
%given by admissibility satisfying the statements that for all $i \in 
%J$, $e_i > \deg z$ for any generator $z$ of $R'$ and that $in_\prec
%(I')$ is minimally generated by products of two monomials under
%some ordering.
%
%Then we can apply two processes of induction, by adding points via
%Proposition ~\ref{prop:sat_three_induction} and by raising
%ramification orders via Theorem ~\ref{thm:ram_order_ind},
%to obtain the desired result for any tame log spin curve $(\sx,
%\Delta, L)$ over a perfect field $k$ with signature $\sigma$
%covered by this induction process.
%
%
%
%A process of induction raising the ramification orders of
%the ramified points of the spin curves corresponding to Lemma
%~\ref{lem:g_0_admissible_cases} cases (a)-(c) via Theorem
%~\ref{thm:ram_order_ind} will demonstrate the desired generator and
%relation degree results for curves with three ramified points.
%Similarly, this induction process on Lemma
%~\ref{lem:g_0_admissible_cases} case (d) will give the desired
%result for curves with four ramified points excluding signature
%$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
%number of ramified points via Proposition
%~\ref{prop:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
%case (e) combined with the induction process on ramification orders
%will yield the result for curves with at least five ramified points.
\end{proof}

>>>>

\begin{lem}
\label{lem:deg1_sat_ind}
Let $X$ be a genus $g$ curve with a $\mathbf{Q}$-divisor $D$ (as
defined by O'Dorney \todo{reference this-Section 1 of Evan's paper, or preferably define it in the background section})
satisfying $\deg(\lfloor{D}\rfloor)\ge 0$.  Suppose $P$ is not a base point of $D$ meaning that $R_D$ has a
generator $u$ in degree 1 that is a section of $\so_D$ with $\ord_P(u)=0$.  Let $D$ be generated by $u, x_1, \ldots, x_m$ in degree at most $\bar{d}$ with relations generated 
in degree at most $\bar{\tau}$.  Suppose $D' = D + \frac{\alpha}{\beta} P$
for some $\alpha,\beta \in \mathbf{N}$ such
that
\begin{equation}
\label{eqn:deg1_sat_ind_dim}
	h^0(X, \lfloor{dD + d\frac{\alpha}{\beta} P \rfloor}) = h^0(X,\lfloor dD
	\rfloor) + \lfloor d\frac{\alpha} {\beta} \rfloor \forall d \in \mathbf{
	N} : d \ge \frac{\beta}{\alpha}.
\end{equation}
Let 
\[
	0<\frac{c_1}{d_1}<...<\frac{c_n}{d_n}=\frac{\alpha}{\beta}
\]
be the non-negative best lower approximation.
Then 
\begin{itemize}
\item $R_{D'}$ is generated over $R_D$ by elements $y_1,...,y_n$ such that $y_i$ lies in  
degree $d_i$ and has a pole at $P$ of degree $c_i$

@@

\begin{align*}
	\initial_\prec(I') &= \initial_\prec(I) k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \\
										 &+ \langle y_i x_j: 1 \le i \le n, 1 \le j \le m \rangle \\
										 &+ \langle y_i y_j: \lfloor \frac{\alpha}{\beta} \rfloor \rangle \le i \le j \le n-1 \\
										 &+ \langle y_i y_j: 1\le i\le j\lfloor \frac{\alpha}{\beta} \rfloor\\
										 &+ \langle (y_i)^{\deg(y_{i+1}+1)}: 1\le i=\lfloor \frac{\alpha}{\beta} \rfloor
\end{align*}
In particular, if $\frac{\alpha}{\beta}\le 1$, then $I$ is minimally generated by elements with leading terms of the form $y_ix_j$ and $y_iy_j$.
%\item If $\gin_\prec(I)=\initial_\prec(I)$ then $\gin_\prec(I')=\initial_\prec(I')$.
\item A Grobner basis with the initial terms $y_i x_j$, $y_iy_j$, and possibly $(y_{\lfloor \frac{\alpha}{\beta} \rfloor})^{y_{\lfloor \frac{\alpha}{\beta} \rfloor}+1}$ as shown above minimally generates $I'$.
\end{itemize}
\end{lem}

@@

\begin{lem}
\label{lem:sat_two_induction}
Let $(\sx, \Delta, \halfcan_\sx)$ and $(\sx', \Delta, \halfcan_{\sx'})$ be log stacky curves with coarse space $(X, \Delta, L_X)$ and signatures $(g; e_1, \ldots, e_r; \delta)$ and $(g, e_1, \ldots, e_{r-1}, \delta)$ respectively, with $g > 0,$ and, if $g = 1$ then $\deg 3L \geq 2$.
Let $R_{L'} = R' = k[x]/I'= k[x_2, x_3
, x_5,\ldots, x_m]/I'$ and let $\halfcan = \halfcan' + \frac{1}{
3}P$, where $P\in X$ is a base point of $\halfcan'$ (which includes the case when $H^0(X,\lfloor \halfcan'\rfloor)=0$.  Suppose $\halfcan$ and $\halfcan'$ satisfy $sat(Eff(\halfcan')) = sat(Eff(\halfcan)) = 2.$
Suppose $\deg x_i = i$ for $i \in \{2, 3\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_2}(f) < \ord_{x_2}(g) \implies f \prec g.
\end{align*}
Then, the following statements hold.
\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3, 4\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4]$ with $grlex$ so that $y_4 \prec 
		y_3$
		and equip the ring $k[y_3, y_4, x]$ with the block 
		order so that $R = k[y_3, y_4, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x, y_3, y_4] \\
			&+\langle y_4 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_4^2.\rangle
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

In a fashion analogous to the proof of Lemma 
~\ref{lem:sat_three_induction}, we see 
the following is a $k$ basis for $R$ over $R'$:

\begin{lem}
\label{lem:sat_two_induction}
\todo{Make explicit assumptions on genus.}
\todo{Should switch either $R$ and $R'$ or $\sx$ and $\sx'$ to make prime notation consistent (note that inclusion is reversed since this map adds a stacky point to $\sx$; note that we should also say that this map is only ramified at $P$), Aaron: you're right, I wrote the inclusion on rings in the wrong direction. Actually, the map isn't ramified at $P$, it's just defined away from $P$. I decided to remove this from the proposition though.} Let $R_{L'} = R' = k[x]/I'= k[x_3, x_4
, x_5,\ldots, x_m]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $L = L' + \frac{1}{
3}P$, and let $R = R_L$. Suppose $\deg x_i = i$ for $i \in \{3, 4, 5\}$ and that the ordering on $k[x]$ satisfies
\begin{align*}
	\ord_{x_3}(f) < \ord_{x_3}(h) \implies f \prec h.
\end{align*}
Then, the following statements hold.

\begin{enumerate}
	\item[(a)] General elements  $y_i \in H^0(\sx,iL)$ for $i \in \{3,
		4,5\}$ satisfy $-\ord_P(y_i) = 1$ and any such choice of elements $y
		_3,y_4,$ and $y_5$ minimally generate $R$ over $R'$.
	\item[(b)] Equip $k[y_3, y_4, y_5]$ with $grlex$ so that $y_5 \prec 
		y_4 \prec y_3$
		and equip the ring $k[y_3, y_4, y_5, x]$ with the block 
		order so that $R = k[y_3, y_4, y_5, x]/I$. Let,
		\begin{align*}
			J &= gin_\prec(I')k[x,y_3,y_4,y_5] \\
			&+\langle y_i x_j \mid 4 \leq i \leq 5, 3 \leq j \leq m\rangle \\
			&+\langle y_iy_k \mid 4 \leq i \leq j \leq 5.\rangle 
		\end{align*}
			Then, $gin_\prec(I) = J$.
	\item[(c)] Any set of minimal generators for $I'$ together with 
		any set of relations with leading terms as in (b) minimally 
		generate $I$.
\end{enumerate}
\end{lem}

\iffalse{
\begin{lem}\label{lem:adding_points_saturation_2_to_1_with_log}
Let $(\sx, \Delta, \halfcan)$ and $(\sx, \Delta', L')$ be tame separably rooted log stacky spin 
curves with $0\ne \Delta=\Delta'+2P$ for some non-stacky point $P$ not in the support of $
\halfcan'$, meaning that $L=L'+P$.  Let $(g; e_1, \ldots, e_\tau; \delta+2)$ and $(g; e_1, 
\ldots, e_\tau, \delta)$ with $g\ge 2$ be their respective signatures.  Suppose 
$sat(Eff(\halfcan))=1$ and $sat(Eff(\halfcan'))=2$.  Further suppose $R_{\halfcan'} = k[x_2, 
x_3, \ldots, x_m]/I'$ with $\deg(x_2) = 2$ and $\deg(x_3) = 3$.  Then
\begin{enumerate}
\item[(a)] Then generic elements $y_1$ and $y_2$ in $(R_{\halfcan})_1$ and $
(R_{\halfcan})_2$ respectively, such that $-\ord_P(y_2)>0$ and $\{y_1^2, y_2\}$ is linearly 
independent, generate $R_\halfcan$ over $R_{\halfcan'}$.
\item[(b)] Equip $k[y_1,y_2]$ with $grlex$ so that $y_2 \prec y_1$ and equip $k[y_1, y_2, 
x_2, \ldots, x_m]$ with the block order so that $R_\halfcan=k[y_1, y_2, x_2, \ldots, x_m]/I$.  
Then
\begin{align*}
			in_\prec(I) &= in_\prec(I')k[x_2, \ldots, x_m, y_1, y_2] \\
			&+\langle y_2 x_j \mid 2 \leq j \leq m \rangle \\
			&+\langle y_2^2\rangle.
		\end{align*}
\item[(c)] Any set of minimal generators for $I'$ together with any set of relations with 
leading terms as above minimally generate $I$.
\end{enumerate}
\end{lem}

@@

}
\fi

@@

In the case of a smooth genus 1 curve, $X$, we know $K_X = 0$, and therefore the only possibilities for half canonical divisors are $\halfcan' = 0$ or $\halfcan' = P-Q$ where $P,Q$ are distinct points, fixed under the hyperelliptic involution. We aim to inductively construct presentations by increasing the values of the $e_i$ using Theorem ~\ref{thm:ram_order_ind} and add additional points using Lemma ~\ref{lem:deg1_sat_ind} and Proposition ~\ref{lem:sat_two_induction}.

@@

\ssec{Base Cases}
\label{ssec:g_0_base}
Now we have an inductive statement on the number of ramified
points in Lemma ~\ref{lem:sat_three_induction} and
an inductive statement on ramification orders in Theorem
~\ref{thm:ram_order_ind}. After verifying that explicit pairs
$(\sx, J)$ of stacky curves $\sx$ with particular signatures and
particular choices of $J$ are admissible, the application of the
two inductive statements demonstrate that the spin canonical ring
$R(\sx , 0, L)$ is generated in degree at most $e := \max(5, e_1,
\ldots, e_r)$ with relations generated in degree at most $2e$ for
$\sx$ with any signature $\sigma = (0; e_1, \ldots , e_r; 0)$ outside
of a finite set of exceptional cases.

@@

Through the application of two processes of induction, by adding 
points via Lemma ~\ref{lem:sat_three_induction} and by raising
ramification orders via Theorem ~\ref{thm:ram_order_ind},
we obtain Theorem ~\ref{thm:g_0_generators_relations} for any tame
log spin curve $(\sx, \Delta, L)$ over a perfect field $k$ with
signature $\sigma$ covered by this induction process.
In particular, this induction process covers all signatures $\sigma
= (0; e_1, \ldots, e_r; 0)$ such that either $r \geq 5$ or
for some listed base case $(\sigma', J)$ with $\sigma' = (0; e_1',
\ldots, e_r'; 0)$, $e_i \geq e_i'$ for all $i$.
Before we prove the main theorem, we describe the cases not be
covered by induction.

@@

Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
If $\sigma = (0; e_1, \ldots, e_r; 0)$ is not one of the
exceptional cases in Table ~\ref{table:g_0_exceptional} and $r \leq
5$, then $\sigma$ ``lies above'' one of the base cases of Lemma
~\ref{lem:g_0_admissible_cases}. In other words, one of the base
cases $(\sigma', J)$ with $\sigma' = (0; e_1', \ldots, e_r'; 0)$
satisfies the property that for all $i \in J$, $e_i \geq e_i'$ and
$e_i = e_i'$ otherwise. If $r > 5$, then we can use Lemma
~\ref{lem:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$, since the
saturation in this case is equal to $3$.

@@

%By Lemma ~\ref{lem:g_0_admissible_cases}, we know that for
%any tame log spin curves $(\sx', \Delta, \halfcan')$ over a perfect
%field $k$ with signature $\sigma'$ and set $J$ such that $(\sigma',
%J)$ is one of the listed base cases, $(\sigma', J)$ is admissible.
%Furthermore, $R' := R(\sx', \Delta, \halfcan')$ is generated as a $k
%$- algebra by elements of degree at most $e = \max(5, e_1, \ldots, e
%_r)$ with relations in degree at most $2e$. It also admits a
%presentation
%
%\begin{align*}
	%R' \cong \left( k[x_1, \ldots, x_m] \otimes k[y_{i,e_i'}]_{i \in J} \right)/I'
%\end{align*}
%
%\noindent
%given by admissibility satisfying the statements that for all $i \in 
%J$, $e_i > \deg z$ for any generator $z$ of $R'$ and that $in_\prec
%(I')$ is minimally generated by products of two monomials under
%some ordering.
%
%Then we can apply two processes of induction, by adding points via
%Lemma ~\ref{lem:sat_two_induction} and by raising
%ramification orders via Theorem ~\ref{thm:ram_order_ind},
%to obtain the desired result for any tame log spin curve $(\sx,
%\Delta, L)$ over a perfect field $k$ with signature $\sigma$
%covered by this induction process.
%
%
%
%A process of induction raising the ramification orders of
%the ramified points of the spin curves corresponding to Lemma
%~\ref{lem:g_0_admissible_cases} cases (a)-(c) via Theorem
%~\ref{thm:ram_order_ind} will demonstrate the desired generator and
%relation degree results for curves with three ramified points.
%Similarly, this induction process on Lemma
%~\ref{lem:g_0_admissible_cases} case (d) will give the desired
%result for curves with four ramified points excluding signature
%$(0; 3, 3, 3, 3; 0)$. A process of induction increasing the
%number of ramified points via Lemma
%~\ref{lem:sat_three_induction} on Lemma ~\ref{lem:g_0_admissible_cases}
%case (e) combined with the induction process on ramification orders
%will yield the result for curves with at least five ramified points.
\end{proof}
